Novel Sampling Using Stochastic Gradient Descent

### 2016-12-05 poster/main.tex
complete content

\begin{itemize}
    \item aaa
\end{itemize}

@@

\begin{figure}
\includegraphics[width=0.4\linewidth]{../figure/simulation2_empirical.png}
\includegraphics[width=0.4\linewidth]{../figure/simulation2_real.png}
\caption{Figure caption}
\end{figure}

@@

\begin{itemize}
    \item aaa
\end{itemize}

>>>>

\begin{itemize}
\item Sampling from posterior distribution is crucial in various statistical techniques
\item Posterior can be hard to sample  (hurdle a lot of applications)
\item SGD can be viewed as a Markov chain
\item Property as a Markov chain seems to be largely overlooked
\item Stationary distribution? Mixing time? Mixing time relationship with convergence rate?
\end{itemize}

@@

\begin{figure}
\includegraphics[width=0.5\linewidth]{../figure/simulation2_empirical.png}
\includegraphics[width=0.5\linewidth]{../figure/simulation2_real.png}
\caption{Figure caption}
\end{figure}

@@

\begin{itemize}
\item Proposed fast SGD sampler for posterior distributions. Computing the likelihood from the full data is intensive.
\item Proved accurate stationary distribution based on oracle results
\item Established connection between SGD and maximize \emph{a posteriori} (MAP)
\item Derived upper bound on mixing time
\item Future work: Finite sample rates of convergence for the mixing time
\end{itemize}
